Correlation tests

### 2025-03-28 analysis/manuscript.qmd
Finish first draft discussion, next introduction

Transformative agreements appeared to be a key driver of national open access growth (see Figure \ref{fig-uptake_country}C and D).
OECD members accounted for the majority of open access articles enabled by transformative agreements.
As a notable exception, South Africa also featured prominently, as the South African National Library and Information Consortium (SANLiC) successfully negotiated transformative agreements with major publishers from 2022 onward.[^sa]
Results were consistent across data sources. 
However, Wiley's open access surplus in hoaddata led to better rankings for countries where Wiley played a substantial role, such as Germany, where the DEAL consortium negotiated its first transformative agreements with Wiley that started in July 2019.

@@

Investigating over 13,000 hybrid journals included in the cOAlition Journal Checker Tool shows a substantial increase in  open access enabled by transformative agreements between 2019 and 2023, although most articles in these journals remained paywalled during this five-year period.
While transformative agreements accounted for the majority of open access, a considerable number of open access articles are likely to have resulted from the payment of individual publication fees.
The results confirm that transformative agreements and hybrid open access continue to be concentrated among a few large commercial publishers.
They also highlight that high-income European countries in particular are using transformative agreements to make most of their article output open access, although South Africa showed similar levels of open access adoption. 
These trends were consistent across the investigated open data source hoaddata, derived from Crossref and OpenAlex, and the established proprietary bibliometric databases Scopus and Web of Science.

Comparing the data sources examined, the study results show strong correlations by country affiliation, despite differences in journal and article coverage, and in the availability of metadata on corresponding authorship and open access status. 
However, several notable discrepancies warrant discussion.
They stem not only from known limitations of the open scholarly metadata sources Crossref and OpenAlex, but also from the proprietary databases Scopus and Web of Science.

The coverage analysis reveals that hybrid journals are well indexed in all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local non-English language communties, with many such titles indexed exclusively in Crossref and Scopus.
Using the open index Crossref demonstrated particular strength in identifying newly established hybrid journals, a notable finding given that transformative agreements primarily target existing subscription-based journals.

@@

A notable advantage of using Scopus and Web of Science to study the impact of transformative agreements is their comprehensive differentiation of journal articles by document type, as many agreements restrict funding to eligible article types. 
This resulted in slightly higher rates of open access uptake compared to hoaddata.

A similar limitation of studying open access with open scholarly data sources is the often reported lack of corresponding authorship information. 
However, indicators using first authors, which have often been used as a proxy for determining open access funding, and corresponding authors show a high level of correlation, which is not surprising given disciplinary norms in scholarly publishing. 
First authors are often considered to have carried out the main research underlying a paper, while the corresponding author is often recognised as having supervised a paper. 
It is therefore not surprising that both are strongly correlated, suggesting that first and corresponding authors share the same country affiliation.
Moreover, in most cases the first author is indeed the same as the corresponding author. As such, first authorship can be used confidentially in large-scale studies and those focusing on national consortia to assess the impact of transformative agreements.

However, affiliation data is sparser in OpenAlex than in Scopus and Web of Science, resulting in slightly more articles that could be attributed to transformative agreements. 
However, in order to establish a link, a thorough mapping of the database affiliation identifier to the ROR ID, the JCT's identifier for institutional participation in transformative agreements, is required.
In contrast, ROR IDs are the canonical organisation identifier in OpenAlex, allowing for less ambiguous matching between agreement and publication.

Comparison of scholarly databases is also valuable in identifying differences in open access identification. 
Not all publishers deposit a Creative Commons licence with Crossref, the citation authority.
A collaboration with Scopus and Web of Science helped to identify such publishers, as their underlying unpaywall data also parses licence information from websites.
However, there were significant differences between Scopus and Web of Science in terms of open access indexing, particularly with regard to the delayed open access provided by Elsevier.
In the case of Wiley, however, there were also problems with the analysis of the Unpaywall.
This suggests that hybrid open access studies should not only refer to a single source of evidence.
Instead, open access tags can be validated by the combiantion of seevral data sources, as in our case where metadata from publishers was compared with data from open access discovery services such as Unpaywall.
It is also particularly useful to include a curated list of journals under the hybrid model to avoid misclassifications based on a journal's business model [@Visser_2021].

@@

<!-- Limitations: agreeemnts are complex, game auhtorship, invoicing not available, mapping, not feasible, requires more insitutional and publsihjer case studies involving financial data, but also improved and streamlined metadata compliance according to the evlolving stadatrd and iniatives (ESAC, Varcelona) in negotiation with publishers.

>>>>

Transformative agreements appeared to be a key driver of national open access growth (see Figure \ref{fig-uptake_country}C and D).
OECD members accounted for the majority of open access articles enabled by transformative agreements.
As a notable exception, South Africa also featured prominently, as the South African National Library and Information Consortium (SANLiC) successfully negotiated transformative agreements with major publishers from 2022 onward.[^sa]
Results were consistent across data sources. 
However, Wiley's open access surplus in hoaddata led to better rankings for countries where Wiley played a substantial role, such as Germany, where the DEAL consortium negotiated its first transformative agreements with publisher that started in July 2019.

@@

This study of over 13,000 hybrid journals included in the cOAlition Journal Checker Tool shows a rise in open access due to transformative agreements between 2019 and 2023, although most articles remained paywalled.
While transformative agreements accounted for the majority of open access, many articles continue to become open through the payment of individual publication fees.
Hybrid open access and transformative agreements remain concentrated among a small group of large commercial publishers, 
with high-income European countries—alongside South Africa—showing high adoption rates.
In contrast, the three most productive countries, China, the United States, and India, were ranked much behind other countries in the adoption of transformative agreements.
These trends were consistent across the investigated open data source hoaddata, derived from Crossref and OpenAlex, and the established proprietary bibliometric databases Scopus and Web of Science.
An open question remains whether this uneven distribution reflects temporary implementation gaps, inherent inequities in the transformative agreement model, or countries voluntarily refraining from such agreements.

Comparing the data sources examined, the study results show strong correlations by country affiliation, despite differences in journal and article coverage, and in the availability of metadata on corresponding authorship and open access status. 
However, several notable discrepancies warrant discussion.
They arise from limitations in both open and proprietary databases.

The coverage analysis reveals that hybrid journals are well indexed in all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local non-English language communities, with many such titles indexed exclusively in Crossref and Scopus.
Using the open index Crossref as bibliometric database in hoaddata demonstrated particular strength in identifying newly established hybrid journals, a notable finding given that transformative agreements primarily target existing subscription-based journals.

@@

A notable advantage of using Scopus and Web of Science to study the impact of transformative agreements is their comprehensive differentiation of journal articles by document type, as many agreements restrict funding to original articles and reviews. 
This resulted in slightly higher open access rates in Scopus and Web of Science.

A similar limitation of studying open access with less selective databases is the often reported lack of corresponding authorship information [@Fraser_2023; @Haucap_2021; @Shu_2023]. 
However, indicators based on first authors, which have often been used as a proxy for determining open access funding, and corresponding authors show a high level of correlation, in line with previous research, reflecting disciplinary norms in scholarly publishing with regard to contributorship and author roles and positions [@Larivi_re_2016]. 
First authors are often considered to have carried out the main research underlying a paper, while the corresponding author is often recognised as having supervised the research [@Mattsson_2010; @Fox_2018]. 
It is therefore not surprising that both are strongly correlated, suggesting that first and corresponding authors share the same country affiliation.
Moreover, in most cases the first author is indeed the same as the corresponding author [@Chinchilla_Rodr_guez_2024].

The slight increase in the number of open access articles by corresponding authors compared to the number of first authors in the last two years observed across Springer Nature hybrid journals raises the question about institutional open access sponsorship practices and if they influence the assignment of author roles among co-authors, especially when funding opportunities are not consistently available within the author teams [@Gumpenberger_2018].
Previous research notes effects of institutionalised bibliometrics praticses on the valuations of authorship positions [@Helgesson_2020], although, to my knowledge, no such evidence was reported for open access funding yet.
As such, first authorship can reliably be used in large-scale studies and those focusing on national consortia to assess the impact of transformative agreements.

While OpenAlex’s affiliation coverage is less complete, it shows strong correlations with Scopus [@Akbaritabar_2024; @alperin2024analysissuitabilityopenalexbibliometric]. 
In this study, this limitation likely reduced the number of articles confidently attributed to transformative agreements, despite high correlations between OpenAlex, Scopus, and Web of Science at the country level. Nevertheless, OpenAlex’s native ROR ID integration offers a distinct advantage: unlike Scopus and Web of Science, which require reconciliation of proprietary organisation identifiers with this open standard, it enables more reliable identification of agreement-enabled articles.
<!-- Dimension is another scholarly data source that uses open standards to identify journals, which enables analysing transformative agreements [@Fraser_2023].-->

Comparing scholarly databases helps to identify  discrepancies in open access evidence. 
Not all publishers deposit CC licences with Crossref, but Unpaywall, integrated into Scopus and Web of Science, can make this transparent, because the open access discovery services also analyse publishers' websites.
However, inconsistencies remain: Web of Science incorrectly identifies Elsevier's delayed open access as hybrid, while Scopus correctly reflects it.
Unpaywall also missed a substantial number of open access articles with CC license according to Crossref, resulting in fewer open access articles in Scopus and Web of Science, probably due to problems parsing the publisher's website.
As these differences may affect comparability between databases, research and monitoring exercises should not rely on a single source of evidence.
Instead, it is recommended that the choice of open access evidence sources should be documented and verified by combining multiple data sources [@Huang_2020].
It is particularly useful to include expert-curated lists of journals to avoid misclassifications based on a journal's business model [@Visser_2021].

It is important to note that articles from institutions involved in transformative agreements are estimates due to a lack of access to invoice data, which is not usually shared between library consortia and publishers. 
Furthermore, it is important to acknowledge that the sources of transformative agreements and the underlying ESAC registry are a voluntary effort, crowd-sourced from various consortia. 
However, recent validation with Dutch Research Information demonstrates the reliability of such an open approach for the assessment of articles under transformative agreements. 
With enhanced and streamlined metadata compliance, attributable to evolving standards and initiatives to support negotiations with publishers, particularly through the communities of the ESAC initiative and Barcelona Declaration supporters, the situation is likely to improve. In conclusion, this cross-database analysis has highlighted the potential and challenges of establishing open scholarly data as a suitable evidence base for analysing the transition from subscription-based publishing to open access.

@@

<!-- Limitations: agreeemnts are complex, game auhtorship, invoicing not available, mapping, not feasible, requires more insitutional and publsihjer case studies involving financial data, but also improved and streamlined metadata compliance according to the evlolving stadatrd and iniatives (ESAC, Barcelona) in negotiation with publishers.

### 2025-03-28 analysis/manuscript.tex
Finish first draft discussion, next introduction

Transformative agreements appeared to be a key driver of national open
access growth (see Figure \ref{fig-uptake_country}C and D). OECD members
accounted for the majority of open access articles enabled by
transformative agreements. As a notable exception, South Africa also
featured prominently, as the South African National Library and
Information Consortium (SANLiC) successfully negotiated transformative
agreements with major publishers from 2022 onward.\footnote{\url{https://sanlic.ac.za/read-and-publish-agreements/}}
Results were consistent across data sources. However, Wiley's open
access surplus in hoaddata led to better rankings for countries where
Wiley played a substantial role, such as Germany, where the DEAL
consortium negotiated its first transformative agreements with Wiley
that started in July 2019.

@@

Investigating over 13,000 hybrid journals included in the cOAlition
Journal Checker Tool shows a substantial increase in open access enabled
by transformative agreements between 2019 and 2023, although most
articles in these journals remained paywalled during this five-year
period. While transformative agreements accounted for the majority of
open access, a considerable number of open access articles are likely to
have resulted from the payment of individual publication fees. The
results confirm that transformative agreements and hybrid open access
continue to be concentrated among a few large commercial publishers.
They also highlight that high-income European countries in particular
are using transformative agreements to make most of their article output
open access, although South Africa showed similar levels of open access
adoption. These trends were consistent across the investigated open data
source hoaddata, derived from Crossref and OpenAlex, and the established
proprietary bibliometric databases Scopus and Web of Science.

Comparing the data sources examined, the study results show strong
correlations by country affiliation, despite differences in journal and
article coverage, and in the availability of metadata on corresponding
authorship and open access status. However, several notable
discrepancies warrant discussion. They stem not only from known
limitations of the open scholarly metadata sources Crossref and
OpenAlex, but also from the proprietary databases Scopus and Web of
Science.

The coverage analysis reveals that hybrid journals are well indexed in
all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local
non-English language communties, with many such titles indexed
exclusively in Crossref and Scopus. Using the open index Crossref
demonstrated particular strength in identifying newly established hybrid
journals, a notable finding given that transformative agreements
primarily target existing subscription-based journals.

@@

A notable advantage of using Scopus and Web of Science to study the
impact of transformative agreements is their comprehensive
differentiation of journal articles by document type, as many agreements
restrict funding to eligible article types. This resulted in slightly
higher rates of open access uptake compared to hoaddata.

A similar limitation of studying open access with open scholarly data
sources is the often reported lack of corresponding authorship
information. However, indicators using first authors, which have often
been used as a proxy for determining open access funding, and
corresponding authors show a high level of correlation, which is not
surprising given disciplinary norms in scholarly publishing. First
authors are often considered to have carried out the main research
underlying a paper, while the corresponding author is often recognised
as having supervised a paper. It is therefore not surprising that both
are strongly correlated, suggesting that first and corresponding authors
share the same country affiliation. Moreover, in most cases the first
author is indeed the same as the corresponding author. As such, first
authorship can be used confidentially in large-scale studies and those
focusing on national consortia to assess the impact of transformative
agreements.

However, affiliation data is sparser in OpenAlex than in Scopus and Web
of Science, resulting in slightly more articles that could be attributed
to transformative agreements. However, in order to establish a link, a
thorough mapping of the database affiliation identifier to the ROR ID,
the JCT's identifier for institutional participation in transformative
agreements, is required. In contrast, ROR IDs are the canonical
organisation identifier in OpenAlex, allowing for less ambiguous
matching between agreement and publication.

Comparison of scholarly databases is also valuable in identifying
differences in open access identification. Not all publishers deposit a
Creative Commons licence with Crossref, the citation authority. A
collaboration with Scopus and Web of Science helped to identify such
publishers, as their underlying unpaywall data also parses licence
information from websites. However, there were significant differences
between Scopus and Web of Science in terms of open access indexing,
particularly with regard to the delayed open access provided by
Elsevier. In the case of Wiley, however, there were also problems with
the analysis of the Unpaywall. This suggests that hybrid open access
studies should not only refer to a single source of evidence. Instead,
open access tags can be validated by the combiantion of seevral data
sources, as in our case where metadata from publishers was compared with
data from open access discovery services such as Unpaywall. It is also
particularly useful to include a curated list of journals under the
hybrid model to avoid misclassifications based on a journal's business
model (Visser et al., 2021).

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Baas_2020}
Baas, J., Schotten, M., Plume, A., Côté, G., \& Karimi, R. (2020).
Scopus as a curated, high-quality bibliometric data source for academic
research in quantitative science studies. \emph{Quantitative Science
Studies}, \emph{1}(1), 377--386.
\url{https://doi.org/10.1162/qss_a_00019}

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Transformative agreements appeared to be a key driver of national open
access growth (see Figure \ref{fig-uptake_country}C and D). OECD members
accounted for the majority of open access articles enabled by
transformative agreements. As a notable exception, South Africa also
featured prominently, as the South African National Library and
Information Consortium (SANLiC) successfully negotiated transformative
agreements with major publishers from 2022 onward.\footnote{\url{https://sanlic.ac.za/read-and-publish-agreements/}}
Results were consistent across data sources. However, Wiley's open
access surplus in hoaddata led to better rankings for countries where
Wiley played a substantial role, such as Germany, where the DEAL
consortium negotiated its first transformative agreements with publisher
that started in July 2019.

@@

This study of over 13,000 hybrid journals included in the cOAlition
Journal Checker Tool shows a rise in open access due to transformative
agreements between 2019 and 2023, although most articles remained
paywalled. While transformative agreements accounted for the majority of
open access, many articles continue to become open through the payment
of individual publication fees. Hybrid open access and transformative
agreements remain concentrated among a small group of large commercial
publishers, with high-income European countries---alongside South
Africa---showing high adoption rates. In contrast, the three most
productive countries, China, the United States, and India, were ranked
much behind other countries in the adoption of transformative
agreements. These trends were consistent across the investigated open
data source hoaddata, derived from Crossref and OpenAlex, and the
established proprietary bibliometric databases Scopus and Web of
Science. An open question remains whether this uneven distribution
reflects temporary implementation gaps, inherent inequities in the
transformative agreement model, or countries voluntarily refraining from
such agreements.

Comparing the data sources examined, the study results show strong
correlations by country affiliation, despite differences in journal and
article coverage, and in the availability of metadata on corresponding
authorship and open access status. However, several notable
discrepancies warrant discussion. They arise from limitations in both
open and proprietary databases.

The coverage analysis reveals that hybrid journals are well indexed in
all three data sources, particularly in terms of article coverage.
Differences can be found for journals targeting practitioners or local
non-English language communities, with many such titles indexed
exclusively in Crossref and Scopus. Using the open index Crossref as
bibliometric database in hoaddata demonstrated particular strength in
identifying newly established hybrid journals, a notable finding given
that transformative agreements primarily target existing
subscription-based journals.

@@

A notable advantage of using Scopus and Web of Science to study the
impact of transformative agreements is their comprehensive
differentiation of journal articles by document type, as many agreements
restrict funding to original articles and reviews. This resulted in
slightly higher open access rates in Scopus and Web of Science.

A similar limitation of studying open access with less selective
databases is the often reported lack of corresponding authorship
information (Fraser et al., 2023; Haucap et al., 2021; Shu \& Larivière,
2023). However, indicators based on first authors, which have often been
used as a proxy for determining open access funding, and corresponding
authors show a high level of correlation, in line with previous
research, reflecting disciplinary norms in scholarly publishing with
regard to contributorship and author roles and positions (Larivière et
al., 2016). First authors are often considered to have carried out the
main research underlying a paper, while the corresponding author is
often recognised as having supervised the research (Fox et al., 2018;
Mattsson et al., 2010). It is therefore not surprising that both are
strongly correlated, suggesting that first and corresponding authors
share the same country affiliation. Moreover, in most cases the first
author is indeed the same as the corresponding author
(Chinchilla-Rodríguez et al., 2024).

The slight increase in the number of open access articles by
corresponding authors compared to the number of first authors in the
last two years observed across Springer Nature hybrid journals raises
the question about institutional open access sponsorship practices and
if they influence the assignment of author roles among co-authors,
especially when funding opportunities are not consistently available
within the author teams (Gumpenberger et al., 2018). Previous research
notes effects of institutionalised bibliometrics praticses on the
valuations of authorship positions (Helgesson, 2020), although, to my
knowledge, no such evidence was reported for open access funding yet. As
such, first authorship can reliably be used in large-scale studies and
those focusing on national consortia to assess the impact of
transformative agreements.

While OpenAlex's affiliation coverage is less complete, it shows strong
correlations with Scopus (Akbaritabar et al., 2024; Alperin et al.,
2024). In this study, this limitation likely reduced the number of
articles confidently attributed to transformative agreements, despite
high correlations between OpenAlex, Scopus, and Web of Science at the
country level. Nevertheless, OpenAlex's native ROR ID integration offers
a distinct advantage: unlike Scopus and Web of Science, which require
reconciliation of proprietary organisation identifiers with this open
standard, it enables more reliable identification of agreement-enabled
articles.

Comparing scholarly databases helps to identify discrepancies in open
access evidence. Not all publishers deposit CC licences with Crossref,
but Unpaywall, integrated into Scopus and Web of Science, can make this
transparent, because the open access discovery services also analyse
publishers' websites. However, inconsistencies remain: Web of Science
incorrectly identifies Elsevier's delayed open access as hybrid, while
Scopus correctly reflects it. Unpaywall also missed a substantial number
of open access articles with CC license according to Crossref, resulting
in fewer open access articles in Scopus and Web of Science, probably due
to problems parsing the publisher's website. As these differences may
affect comparability between databases, research and monitoring
exercises should not rely on a single source of evidence. Instead, it is
recommended that the choice of open access evidence sources should be
documented and verified by combining multiple data sources (Huang et
al., 2020). It is particularly useful to include expert-curated lists of
journals to avoid misclassifications based on a journal's business model
(Visser et al., 2021).

It is important to note that articles from institutions involved in
transformative agreements are estimates due to a lack of access to
invoice data, which is not usually shared between library consortia and
publishers. Furthermore, it is important to acknowledge that the sources
of transformative agreements and the underlying ESAC registry are a
voluntary effort, crowd-sourced from various consortia. However, recent
validation with Dutch Research Information demonstrates the reliability
of such an open approach for the assessment of articles under
transformative agreements. With enhanced and streamlined metadata
compliance, attributable to evolving standards and initiatives to
support negotiations with publishers, particularly through the
communities of the ESAC initiative and Barcelona Declaration supporters,
the situation is likely to improve. In conclusion, this cross-database
analysis has highlighted the potential and challenges of establishing
open scholarly data as a suitable evidence base for analysing the
transition from subscription-based publishing to open access.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Akbaritabar_2024}
Akbaritabar, A., Theile, T., \& Zagheni, E. (2024). Bilateral flows and
rates of international migration of scholars for 210 countries for the
period 1998-2020. \emph{Scientific Data}, \emph{11}(1).
\url{https://doi.org/10.1038/s41597-024-03655-9}

\bibitem[\citeproctext]{ref-alperin2024analysissuitabilityopenalexbibliometric}
Alperin, J. P., Portenoy, J., Demes, K., Larivière, V., \& Haustein, S.
(2024). An analysis of the suitability of OpenAlex for bibliometric
analyses. \emph{arXiv}. \url{https://arxiv.org/abs/2404.17663}

\bibitem[\citeproctext]{ref-Baas_2020}
Baas, J., Schotten, M., Plume, A., Côté, G., \& Karimi, R. (2020).
Scopus as a curated, high-quality bibliometric data source for academic
research in quantitative science studies. \emph{Quantitative Science
Studies}, \emph{1}(1), 377--386.
\url{https://doi.org/10.1162/qss_a_00019}

@@

\bibitem[\citeproctext]{ref-Chinchilla_Rodr_guez_2024}
Chinchilla-Rodríguez, Z., Costas, R., Robinson-García, N., \& Larivière,
V. (2024). Examining the quality of the corresponding authorship field
in {Web of Science} and {Scopus}. \emph{Quantitative Science Studies},
\emph{5}(1), 76--97. \url{https://doi.org/10.1162/qss_a_00288}

@@

\bibitem[\citeproctext]{ref-Fox_2018}
Fox, C. W., Ritchey, J. P., \& Paine, C. E. T. (2018). Patterns of
authorship in ecology and evolution: First, last, and corresponding
authorship vary with gender and geography. \emph{Ecology and Evolution},
\emph{8}(23), 11492--11507. \url{https://doi.org/10.1002/ece3.4584}

\bibitem[\citeproctext]{ref-Fraser_2023}
Fraser, N., Hobert, A., Jahn, N., Mayr, P., \& Peters, I. (2023). No
deal: German researchers' publishing and citing behaviors after big deal
negotiations with {Elsevier}. \emph{Quantitative Science Studies},
\emph{4}(2), 325--352. \url{https://doi.org/10.1162/qss_a_00255}

@@

\bibitem[\citeproctext]{ref-Gumpenberger_2018}
Gumpenberger, C., Hölbling, L., \& Gorraiz, J. I. (2018). On the issues
of a {``corresponding author''} field-based monitoring approach for gold
open access publications and derivative cost calculations.
\emph{Frontiers in Research Metrics and Analytics}, \emph{3}.
\url{https://doi.org/10.3389/frma.2018.00001}

\bibitem[\citeproctext]{ref-Haucap_2021}
Haucap, J., Moshgbar, N., \& Schmal, W. B. (2021). The impact of the
{German {``DEAL''}} on competition in the academic publishing market.
\emph{Managerial and Decision Economics}, \emph{42}(8), 2027--2049.
\url{https://doi.org/10.1002/mde.3493}

@@

\bibitem[\citeproctext]{ref-Helgesson_2020}
Helgesson, G. (2020). Authorship order and effects of changing
bibliometrics practices. \emph{Research Ethics}, \emph{16}(1--2), 1--7.
\url{https://doi.org/10.1177/1747016119898403}

@@

\bibitem[\citeproctext]{ref-Huang_2020}
Huang, C.-K., Neylon, C., Hosking, R., Montgomery, L., Wilson, K.,
Ozaygen, A., \& Brookes-Kenworthy, C. (2020). \emph{Evaluating
institutional open access performance: Sensitivity analysis}.
\url{https://doi.org/10.1101/2020.03.19.998542}

@@

\bibitem[\citeproctext]{ref-Larivi_re_2016}
Larivière, V., Desrochers, N., Macaluso, B., Mongeon, P., Paul-Hus, A.,
\& Sugimoto, C. R. (2016). Contributorship and division of labor in
knowledge production. \emph{Social Studies of Science}, \emph{46}(3),
417--435. \url{https://doi.org/10.1177/0306312716650046}

@@

\bibitem[\citeproctext]{ref-Mattsson_2010}
Mattsson, P., Sundberg, C. J., \& Laget, P. (2010). Is correspondence
reflected in the author position? A bibliometric study of the relation
between corresponding author and byline position. \emph{Scientometrics},
\emph{87}(1), 99--105. \url{https://doi.org/10.1007/s11192-010-0310-9}

@@

\bibitem[\citeproctext]{ref-Shu_2023}
Shu, F., \& Larivière, V. (2023). The oligopoly of open access
publishing. \emph{Scientometrics}, \emph{129}(1), 519--536.
\url{https://doi.org/10.1007/s11192-023-04876-2}
